Open-Set Domain Adaptation through Self-Supervision

### 2022-02-11 paper/main.tex
small fix

Summarizing, in OSDA tasks, we have both a domain gap ($p_s \neq p_t^{\mathcal{C}_s}$)
and a category gap ($\mathcal{C}_s \neq \mathcal{C}_t$). Moreover, the goal is to assign the target samples either to a category ${i \in \mathcal{C}_s}$,
or to reject them as {\it unknown}.
A metric to measure the complexity of the OSDA problem is the {\it openness} betweeen the source and the target domain \cite{bendale2015open}, 
defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.
When $\mathbb{O} > 0$, we are dealing with an OSDA problem, otherwise we are in a CSDA setting.

>>>>

Summarizing, in OSDA tasks, we have both a domain gap ($p_s \neq p_t^{\mathcal{C}_s}$)
and a category gap ($\mathcal{C}_s \neq \mathcal{C}_t$). Moreover, the goal is to assign the target samples either to a category ${i \in \mathcal{C}_s}$,
or to reject them as {\it unknown}.
A metric to measure the complexity of an OSDA problem is the {\it openness} betweeen the source and the target domain \cite{bendale2015open}, 
defined as $\displaystyle \mathbb{O} = 1-\frac{\mathcal{C}_s}{\mathcal{C}_t}$.
When $\mathbb{O} > 0$, we are dealing with an OSDA problem, otherwise we are in a CSDA setting.
